Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-10-23 documentation/authors.tex
Lots of minor edits

\author{B.~Matusch}
\affil{SNOLAB, Lively, Ontario, P3Y 1N2, Canada}

\author{C.~Amole}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{M.~Ardid}
\affil{Departament de F\'isica Aplicada, IGIC - Universitat Polit\`ecnica de Val\`encia, Gandia 46730 Spain}

\author{I.~J.~Arnquist}
\affil{Pacific Northwest National Laboratory, Richland, Washington 99354, USA}

\author{D.~M.~Asner}
%\affil{Brookhaven National Laboratory, Upton, New York 11973, USA}
\affil{Pacific Northwest National Laboratory, Richland, Washington 99354, USA}

\author{D.~Baxter}
\affil{
Department of Physics and Astronomy, Northwestern University, Evanston, Illinois 60208, USA}
\affil{Enrico Fermi Institute, KICP and Department of Physics, 
University of Chicago, Chicago, Illinois 60637, USA}
%\affil{Fermi National Accelerator Laboratory, Batavia, Illinois 60510, USA}

\author{E.~Behnke}
\affil{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

%\author{P.~Bhattacharjee}
%\affil{Astroparticle Physics and Cosmology Division, Saha Institute of Nuclear Physics, Kolkata, India}

%\author{H.~Borsodi}
%\affil{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

%\author{M.~Bou-Cabo}
%\affil{Departament de F\'isica Aplicada, IGIC - Universitat Polit\`ecnica de Val\`encia, Gandia 46730 Spain}

\author{M.~Bressler}
\affil{Department of Physics, Drexel University, Philadelphia, Pennsylvania 19104, USA}

\author{B.~Broerman}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

%\author{P.~Campion}
%\affil{Department of Physics, Drexel University, Philadelphia, Pennsylvania 19104, USA}

\author{G.~Cao}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{C.~J.~Chen}
\affil{
Department of Physics and Astronomy, Northwestern University, Evanston, Illinois 60208, USA}

\author{U.~Chowdhury}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{K.~Clark}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}
%\affil{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}
%\affil{SNOLAB, Lively, Ontario, P3Y 1N2, Canada}

\author{J.~I.~Collar}
\affil{Enrico Fermi Institute, KICP and Department of Physics,
University of Chicago, Chicago, Illinois 60637, USA}

\author{P.~S.~Cooper}
\affil{Fermi National Accelerator Laboratory, Batavia, Illinois 60510, USA}

\author{M.~Crisler}
\affil{Fermi National Accelerator Laboratory, Batavia, Illinois 60510, USA}
\affil{Pacific Northwest National Laboratory, Richland, Washington 99354, USA}

\author{G.~Crowder}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{N.A.~Cruz-Venegas}
\affil{Instituto de F\'isica, Universidad Nacional Aut\'onoma de M\'exico, M\'exico D.\:F. 01000, M\'exico}

\author{C.~E.~Dahl}
\affil{
Department of Physics and Astronomy, Northwestern University, Evanston, Illinois 60208, USA}
\affil{Fermi National Accelerator Laboratory, Batavia, Illinois 60510, USA}

\author{M.~Das}
\affil{Astroparticle Physics and Cosmology Division, Saha Institute
of Nuclear Physics, Kolkata, India}

\author{S.~Fallows}
\affil{Department of Physics, University of Alberta, Edmonton, T6G 2E1, Canada}

\author{J.~Farine}
\affil{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}

\author{I.~Felis}
\affil{Departament de F\'isica Aplicada, IGIC - Universitat Polit\`ecnica de Val\`encia, Gandia 46730 Spain}

\author{R.~Filgas}
\affil{Institute of Experimental and Applied Physics, Czech Technical University in Prague, Prague, Cz-12800, Czech Republic}

\author{F.~Girard}
\affil{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}
\affil{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, H3C 3J7, Canada}

\author{G.~Giroux}
% \email{ggiroux@owl.phy.queensu.ca}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{J.~Hall}
%\affil{Pacific Northwest National Laboratory, Richland, Washington 99354, USA}
\affil{SNOLAB, Lively, Ontario, P3Y 1N2, Canada}

\author{C.~Hardy}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{O.~Harris}
\affil{Northeastern Illinois University, Chicago, Illinois 60625, USA}

\author{E.~W.~Hoppe}
\affil{Pacific Northwest National Laboratory, Richland, Washington 99354, USA}

\author{M.~Jin}
\affil{
Department of Physics and Astronomy, Northwestern University, Evanston, Illinois 60208, USA}

\author{L.~Klopfenstein}
\affil{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

\author{C.~B.~Krauss}
\affil{Department of Physics, University of Alberta, Edmonton, T6G 2E1, Canada}

\author{M.~Laurin}
\affil{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, H3C 3J7, Canada}

\author{I.~Lawson}
\affil{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}
\affil{SNOLAB, Lively, Ontario, P3Y 1N2, Canada}

\author{A.~Leblanc}
\affil{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}

\author{I.~Levine}
\affil{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

\author{W.~H.~Lippincott}
\affil{Fermi National Accelerator Laboratory, Batavia, Illinois 60510, USA}

\author{F.~Mamedov}
\affil{Institute of Experimental and Applied Physics, Czech Technical University in Prague, Prague, Cz-12800, Czech Republic}

\author{D.~Maurya}
\affil{Bio-Inspired Materials and Devices Laboratory (BMDL), Center for Energy Harvesting Material and Systems (CEHMS), Virginia Tech, Blacksburg, Virginia 24061, USA}

\author{P.~Mitra}
\affil{Department of Physics, University of Alberta, Edmonton, T6G 2E1, Canada}

\author{C.~Moore}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{T.~Nania}
\affil{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

\author{R.~Neilson}
\affil{Department of Physics, Drexel University, Philadelphia, Pennsylvania 19104, USA}

\author{A.~J.~Noble}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{P.~Oedekerk}
\affil{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

%\author{S.~Olson}
%\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{A.~Ortega}
\affil{Enrico Fermi Institute, KICP and Department of Physics,
University of Chicago, Chicago, Illinois 60637, USA}

\author{M.-C.~Piro}
\affil{Department of Physics, University of Alberta, Edmonton, T6G 2E1, Canada}

\author{A.~Plante}
\affil{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, H3C 3J7, Canada}

\author{R.~Podviyanuk}
\affil{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}

\author{S.~Priya}
\affil{Bio-Inspired Materials and Devices Laboratory (BMDL), Center for Energy Harvesting Material and Systems (CEHMS), Virginia Tech, Blacksburg, Virginia 24061, USA}

\author{A.~E.~Robinson}
\affil{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, H3C 3J7, Canada}
%\affil{Fermi National Accelerator Laboratory, Batavia, Illinois 60510, USA}

%\author{A.~Roeder}
%\affil{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

%\author{R.~Rucinski}
%\affil{Fermi National Accelerator Laboratory, Batavia, Illinois 60510, USA}

\author{S.~Sahoo}
\affil{Astroparticle Physics and Cosmology Division, Saha Institute
of Nuclear Physics, Kolkata, India}

\author{O.~Scallon}
\affil{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}

\author{S.~Seth}
\affil{Astroparticle Physics and Cosmology Division, Saha Institute
of Nuclear Physics, Kolkata, India}

\author{A.~Sonnenschein}
\affil{Fermi National Accelerator Laboratory, Batavia, Illinois 60510, USA}

\author{N.~Starinski}
\affil{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, H3C 3J7, Canada}

\author{I.~\v{S}tekl}
\affil{Institute of Experimental and Applied Physics, Czech Technical University in Prague, Prague, Cz-12800, Czech Republic}

\author{T.~Sullivan}
\affil{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author{F.~Tardif}
\affil{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, H3C 3J7, Canada}

\author{E.~V\'azquez-J\'auregui}
\affil{Instituto de F\'isica, Universidad Nacional Aut\'onoma de M\'exico, M\'exico D.\:F. 01000, M\'exico}
\affil{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}

\author{N.~Walkowski}
\affil{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

%\author{J.~Wells}
%\affil{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

\author{U.~Wichoski}
\affil{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}

\author{Y.~Yan}
\affil{Bio-Inspired Materials and Devices Laboratory (BMDL), Center for Energy Harvesting Material and Systems (CEHMS), Virginia Tech, Blacksburg, Virginia 24061, USA}

\author{V.~Zacek}
\affil{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, H3C 3J7, Canada}

\author{J.~Zhang}
\affil{
Department of Physics and Astronomy, Northwestern University, Evanston, Illinois 60208, USA}

>>>>

\author[1]{B.~Matusch}
\affil[1]{SNOLAB, Lively, Ontario, P3Y 1N2, Canada}

\author[2]{C.~Amole}
\affil[2]{Department of Physics, Queen's University, Kingston, K7L 3N6, Canada}

\author[3]{M.~Ardid}
\affil{Departament de F\'isica Aplicada, IGIC - Universitat Polit\`ecnica de Val\`encia, Gandia 46730 Spain}

\author[4]{I.~J.~Arnquist}
\affil[5]{Pacific Northwest National Laboratory, Richland, Washington 99354, USA}

\author[4]{D.~M.~Asner}

\author[5, 6]{D.~Baxter}
\affil[5]{Department of Physics and Astronomy, Northwestern University, Evanston, Illinois 60208, USA}
\affil[6]{Enrico Fermi Institute, KICP and Department of Physics, University of Chicago, Chicago, Illinois 60637, USA}

\author[7]{E.~Behnke}
\affil[7]{Department of Physics, Indiana University South Bend, South Bend, Indiana 46634, USA}

\author[8]{M.~Bressler}
\affil[8]{Department of Physics, Drexel University, Philadelphia, Pennsylvania 19104, USA}

\author[2]{B.~Broerman}

\author[2]{G.~Cao}

\author[5]{C.~J.~Chen}

\author[2]{U.~Chowdhury}

\author[2]{K.~Clark}

\author[6]{J.~I.~Collar}

\author[9]{P.~S.~Cooper}
\affil[9]{Fermi National Accelerator Laboratory, Batavia, Illinois 60510, USA}

\author[4, 9]{M.~Crisler}

\author[2]{G.~Crowder}

\author[10]{N.A.~Cruz-Venegas}
\affil[10]{Instituto de F\'isica, Universidad Nacional Aut\'onoma de M\'exico, M\'exico D.\:F. 01000, M\'exico}

\author[5, 9]{C.~E.~Dahl}

\author[11]{M.~Das}
\affil[11]{Astroparticle Physics and Cosmology Division, Saha Institute of Nuclear Physics, Kolkata, India}

\author[12]{S.~Fallows}
\affil[12]{Department of Physics, University of Alberta, Edmonton, T6G 2E1, Canada}

\author[13]{J.~Farine}
\affil[13]{Department of Physics, Laurentian University, Sudbury, P3E 2C6, Canada}

\author[3]{I.~Felis}

\author[14]{R.~Filgas}
\affil[14]{Institute of Experimental and Applied Physics, Czech Technical University in Prague, Prague, Cz-12800, Czech Republic}

\author[13, 15]{F.~Girard}
\affil[15]{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, H3C 3J7, Canada}

\author[2]{G.~Giroux}

\author[1]{J.~Hall}

\author[2]{C.~Hardy}

\author[16]{O.~Harris}
\affil[16]{Northeastern Illinois University, Chicago, Illinois 60625, USA}

\author[4]{E.~W.~Hoppe}

\author[5]{M.~Jin}

\author[7]{L.~Klopfenstein}

\author[12]{C.~B.~Krauss}

\author[15]{M.~Laurin}

\author[1, 13]{I.~Lawson}

\author[13]{A.~Leblanc}

\author[7]{I.~Levine}

\author[9]{W.~H.~Lippincott}

\author[14]{F.~Mamedov}

\author[17]{D.~Maurya}
\affil[17]{Bio-Inspired Materials and Devices Laboratory (BMDL), Center for Energy Harvesting Material and Systems (CEHMS), Virginia Tech, Blacksburg, Virginia 24061, USA}

\author[12]{P.~Mitra}

\author[2]{C.~Moore}

\author[7]{T.~Nania}

\author[8]{R.~Neilson}

\author[2]{A.~J.~Noble}

\author[7]{P.~Oedekerk}

\author[6]{A.~Ortega}

\author[12]{M.-C.~Piro}

\author[15]{A.~Plante}

\author[13]{R.~Podviyanuk}

\author[17]{S.~Priya}

\author[15]{A.~E.~Robinson}

\author[11]{S.~Sahoo}

\author[13]{O.~Scallon}

\author[11]{S.~Seth}

\author[9]{A.~Sonnenschein}

\author[15]{N.~Starinski}

\author[14]{I.~\v{S}tekl}

\author[2]{T.~Sullivan}

\author[15]{F.~Tardif}

\author[10, 13]{E.~V\'azquez-J\'auregui}

\author[7]{N.~Walkowski}

\author[13]{U.~Wichoski}

\author[17]{Y.~Yan}

\author[15]{V.~Zacek}

\author[5]{J.~Zhang}

### 2018-10-23 documentation/paper.tex
Minor formatting resolutions
Lots of minor edits

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}

@@

@@

The lowest-level data derived from the piezos is the raw waveform $\omega$. This consists of a series of samples collected every $2.5 \times 10^{-6}$ seconds. They are each represented as a 16-bit integer. Only the section of the audio between sample 90,000 (inclusive) and sample 190,000 (exclusive) was used during most experiments, because there is only background noise prior to this window, and a clipped signal produced by hydraulics repressurizing the vessel after. (These sections contain no information and can be undesirably fit on by neural networks.)

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{audio}
    \caption{\label{} An example of the cropped audio waveform $\omega$ (on the left) and full resolution Fourier transform $\beta_{50,001}$ (on the right) for both audio channels. Recorded on 2016-12-02, run 1, event 21.}
\end{figure}

@@

For each event that is captured, four cameras within the PICO-60 apparatus each capture a sequence of 71 images before and after formation of a bubble is detected using the cameras and an image-based trigger. These raw images contain a large amount of extraneous information; they encompass the entire vessel. To reduce the input information, the image window sequence $\iota$ includes 50\texttimes50 cropped windows around the position of the bubble. The 71 frames, many of which contain either no bubble or a bubble in later stages of formation, are reduced to 10 immediately around the formation of the bubble. Five frames from before the recording trigger are included in $\iota$, because the bubble does not cause a trigger until it is already of a significant size.

@@

The initial data set $D$ to which these cuts are applied consists of all events recorded during PICO-60 run 2, between 2016-09-02 and 2017-06-20.

@@

\begin{itemize}
    \item The run was not collected during engineering or testing
    \item Recording was triggered by the camera
    \item AP is not erroneously large and negative ($log_{10}(AP)>-100$)
    \item Recorded more than 25 seconds after reaching target pressure
    \item The bubble position $\chi$ was successfully calculated ($[\chi_{X}, \chi_{Y}, \chi_{Z}]\neq[-100, -100, -100]$)
\end{itemize}

@@

PICO-60 events which include multiple bubbles are \textit{always} neutron events; alpha particles and WIMP candidates never scatter. Thus, no discriminator is required to handle these events, so they are removed. The bubble multiplicity cut $MultiCut(D)$ consists of the following restrictions:

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}
\usepackage{lineno}
\linenumbers

@@

\pagebreak

@@

The lowest-level data derived from the piezos is the raw waveform $\omega$. This consists of a series of samples, collected at the rate of one per microsecond. They are each represented as a 16-bit integer. Only the section of the audio between sample 90,000 (inclusive) and sample 190,000 (exclusive) was used during most experiments, because there is only background noise prior to this window, and a clipped signal produced by hydraulics repressurizing the vessel after. (These sections contain no information and can be undesirably fit on by neural networks.)

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{audio}
    \caption{\label{} An example of the cropped audio waveform $\omega$ (left) and full resolution Fourier transform $\beta_{50,001}$ (right) for both audio channels. Recorded on 2016-12-02, run 1, event 21.}
\end{figure}

@@

For each event that is captured, four cameras within the PICO-60 apparatus each capture a sequence of 41 images before and after formation of a bubble is detected using the cameras and an image-based trigger. These raw images contain a large amount of extraneous information; they encompass the entire vessel. To reduce the input information, the image window sequence $\iota$ includes 50\texttimes50 cropped windows around the position of the bubble. The 41 frames, many of which contain either no bubble or a bubble in later stages of formation, are reduced to 10 immediately around the formation of the bubble. Five frames from before the recording trigger are included in $\iota$, because the bubble does not cause a trigger until it is already of a significant size.

@@

The initial data set $D$ to which these cuts are applied consists of all events recorded in the PICO-60 detector between 2016-09-02 and 2017-06-20.

@@

\begin{itemize}
    \item The run was not collected during engineering or testing
    \item The recording process was triggered by the camera (as opposed to a manual trigger, et cetera)
    \item AP is not erroneously large and negative ($log_{10}(AP)>-100$)
    \item The event was recorded more than 25 seconds after reaching target pressure
    \item The bubble position $\chi$ was successfully calculated ($[\chi_{X}, \chi_{Y}, \chi_{Z}]\neq[-100, -100, -100]$)
\end{itemize}

@@

PICO-60 events which include multiple bubbles are \textit{always} neutron events; alpha particles and WIMP candidates never multiply scatter. Thus, no discriminator is required to handle these events, so they are removed. The bubble multiplicity cut {\it MultiCut}$(D)$ consists of the following restrictions:
